% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{multicol}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Dario Toman}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, development, conflict, political economy},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7in, 9.5in},
  left=0.75in,
  top=0.75in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
%\renewenvironment{itemize}{
 % \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}

\setlist[itemize]{label={}, leftmargin=1em}


\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.2in}
\hline
\vspace{0.05in}
\begin{minipage}{0.5\linewidth}
  \href{https://www.utoronto.ca}{University of Toronto} \\
  \href{https://www.economics.utoronto.ca}{Department of Economic}\\\
  Max Gluskin House\\
  150 St George St, Toronto, ON M5S 2E9
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{tabular}{ll}
    Phone: & +1 (647) 717 - 0767 \\
    Email: & \href{mailto:dario.toman@mail.utoronto.ca}{\tt dario.toman@mail.utoronto.ca} \\
    Homepage: & \href{http://www.dariotoman.com}{\tt www.dariotoman.com} \\
   	CV Version: & \today  \\
  \end{tabular}
\end{minipage}
\vspace{0.01in}
%\hline
\vspace{0.01in}

\textbf{Research Interests:} Applied Microeconomics, Health Economics, Political Economy, Development Economics\\
\textbf{Citizenships:} Canadian, Hungarian (EU), Serbian\\
\textbf{Languages:} English (\textit{Nat.}), Serbian (\textit{Nat.}), Hungarian (\textit{Nat.}), French (\textit{Adv.}), German (\textit{Int.}), Spanish (\textit{Beg.})
\vspace{0.05in}
\hline

\section*{Education}

\begin{itemize}[itemsep=0.5pt]

  \item \textbf{PhD Economics}, \textit{University of Toronto}, \textit{Expected 2026}.
  \begin{itemize}[nosep, topsep=-1em]
  \item Committee: Gustavo J. Bobonis (Supervisor), Ceren Baysan, Rob Gillezeau
  \end{itemize}
  \item \textbf{Visiting Student Research Collaborator}, \textit{Princeton University}, \textit{Winter/Spring 2023}.
    \begin{itemize}[nosep, topsep=-1em]
  	\item Center for Health and Wellbeing
  	\end{itemize}
  	
  \item \textbf{MA Economics}, \textit{University of Toronto}, \textit{2019}.

  \item \textbf{Hons. BA Economics} (Major), \textbf{Mathematics} (Minor), \textbf{German} (Minor),   \textit{University of Toronto}, \textit{2018}.
  
  \item Other Coursework: 
  \begin{itemize}[nosep, topsep=-1em]
  \item Graduate Course in Peace Research, \textit{University of Oslo} and \textit{Peace Research Institute of Oslo, 2017}.
  \end{itemize}
\end{itemize}



\section*{Research}
\begin{itemize}[itemsep=0.5pt]
\item \textbf{Job Market Paper}
\end{itemize}
\begin{list}{}%
{\leftmargin=3em \itemindent=-1em \topsep=0em}
\item "Partisan Elections, Competition, and Candidate Selection: Evidence from School Boards" 
\end{list}
\begin{itemize}[itemsep=0.5pt]
\item \textbf{Working Papers}
\end{itemize}
\begin{list}{}%
{\leftmargin=3em \itemindent=-1em \topsep=0em}
\item "Improving Judicial Protection in Intimate Partner Violence Cases: The Role of Specialized Courts and Judges." \\ \textit{With Carolina Arteaga, Gustavo J. Bobonis and  Paola Salardi}. \\Revise and Resubmit, \textit{Review of Economics and Statistics}.
\item "Electoral Cycles in Female Sterilization." \\ \textit{With Simeon Nichter}. \\ Revise and Resubmit, \textit{World Development.}
\item ``Poppy Bloom and Bust: Violence and Poverty During the Mexican Opium Crisis.''

\end{list}

\begin{itemize}[itemsep=0.5pt]
\item \textbf{Published Non-Peer Reviewed Work}
\end{itemize}
\begin{list}{}%
{\leftmargin=3em \itemindent=-1em \topsep=0em}

\item "Local Manufacturing in a Conflict Zone: Lessons from the White Helmets' PPE Project" \\
\textit{With Carolina Canepari, Isabel Davis, Kristyn Lee, and Stanley Zlotkin.} Reach Alliance, 2022. %Access \href{https://reachalliance.org/news/case-study/syrian-white-helmets-manufacturing-ppe-in-a-conflict-zone/}{\textit{here}}.

\item "\#AUEU: A Twitter analysis of the AU-EU summit 2017." \\ \textit{With  Alexander Gaus.} African Policy Circle, 2018. %Access \href{https://www.gppi.net/media/APC_2018__AUEU_Twitter_Analysis.pdf}{\textit{here}}.
\end{list}

\begin{itemize}[itemsep=0.5pt]
\item \textbf{Presentations}
\end{itemize}
\begin{list}{}%
{\leftmargin=3em \itemindent=-1em \topsep=0em \itemsep=0pt}
\item \textbf{2025:} Canadian Economics Association (CEA) Annual Conference, Workshop on Firms and Inclusive Economic Growth (Queen's University), Banff Empirical Microeconomics Workshop (University of Calgary), University of Toronto (\emph{SWEAT}, Emp. Micro. Brown Bag)
\item \textbf{2024:} University of Toronto (Emp. Micro. Brown Bag)
\item \textbf{2023:} Princeton, American Society of Health Economists Annual Conference
\item \textbf{2022:} Latin American and Caribbean Economic Association Annual Meeting, Reach Symposium (Munk School of Global Affairs)
\item \textbf{2021:} University of Toronto (Emp. Micro. Brown Bag)
\end{list}





\section*{Awards}
\begin{itemize}[nosep, topsep=0pt]
	\item Shortlisted Candidate for TATP TA Teaching Excellence Award, \textit{2023}.
	\item Social Sciences and Humanities Research Council (SSHRC) Doctoral Fellowship, (4$\times$\$20,000), \textit{2021} -- 2024 .
	\item Mobilizing Insights in Defence and Security (MINDS) Doctoral Award, (\$35,000), \textit{2020 -- 2021}.
	\item University of Toronto Doctoral Fellowship. (5$\times$\$17,000), \textit{2019} -- .
\end{itemize}



\section*{Experience}

\begin{itemize}
\item \textbf{Reach Alliance, Munk School of Global Affairs and Public Policy}, Researcher, \textit{2021 --  2023}.




\item \textbf{Global Public Policy Institute} (Berlin), Research Intern -- Peace and Security Group, \textit{2017}.
%\begin{itemize}[nosep, topsep=0em, label={-}, leftmargin=2em]
%\item Performed  literature review and background research in areas including foreign policy, maritime security, conflict prevention, peace building, and conflict sensitive development aid for use in public policy reports and books.
%\item Designed survey and executed statistical analysis for a mixed-methodology report commissioned by the German Ministry of Foreign Affairs.
%\item Co-authored technical report published by the African Policy Circle examining the AU-EU Summit.
%\end{itemize}
\item \textbf{University of Toronto Economic Review}, \textit{2015} -- \textit{2018}.
\begin{itemize}[nosep, topsep=-1em]
  \item    Editor-in-Chief (2018 Issue), Managing Editor (2017 issue), Editor (2016 issue)
\end{itemize}
%\begin{itemize}[nosep, topsep=0em, label={-}, leftmargin=2em]
%\item Collaboratively selected, peer reviewed and edited undergraduate research papers on various Economics topics from over 50 submissions from across North America.
%\item Conducted coding review using Stata, typeset and prepared journal for print using LaTeX.
%\end{itemize}
\end{itemize}
%
%\subsection*{Programming Skills}
%\begin{itemize}[topsep=0pt]
%  \item	STATA, R, Python, Visual Basic, LaTeX, Gephi, ArcGIS, QGIS
%\end{itemize}
%





\section*{Teaching}
\subsection*{Course Instructor}
\begin{itemize}[nosep]
\item {\tt PPG201} - Microeconomics for Engineers, \textit{Fall 2024}.
 \item {\tt PCJ260} - Introduction to Peace, Conflict and Justice I: Data and Applications, \textit{Fall 2023}.
\end{itemize}

\subsection*{Teaching Assistantships}
\begin{itemize}[nosep]
 \item	{\tt ECO334} -- Political Economy of Media, \textit{Winter 2019, Winter 2024, Winter 2025}.
\item {\tt GLA1010} -- Microeconomics for Global Affairs, \textit{Fall 2023, Fall 2024, Fall 2025}.
\item {\tt GLA2060} -- Topics in Development I, \textit{Fall 2021, Fall 2022} [@ \href{https://munkschool.utoronto.ca/mga/}{\tt Munk School MGA}].
     \item {\tt ECO372} -- Data Analysis and Applied Econometrics in Practice, \textit{Fall 2022}.
  \item {\tt PCJ360} -- Topics in Peace, Conflict, and Justice, \textit{Fall 2022}.
  \item {\tt PCJ260} -- Introduction to Peace, Conflict and Justice I: Data and Applications, \textit{Fall 2022}.
 \item {\tt ECO102} -- Principles of Macroeconomics, \textit{Winter 2020 }[Head TA],  \textit{Winter 2021 }[Head TA], \textit{Winter 2022 }[Head TA].
  \item {\tt ECO368} -- Economics of Conflict, \textit{Winter 2020} \textit{Fall 2021}.
  \item {\tt PCJ460} -- Causes and Consequences of Civil War, \textit{Fall 2020}.
  \item {\tt ECO403} -- Topics in Development, \textit{Fall 2018}, \textit{Fall 2019}.
  \item	{\tt ECO324} -- Economic Development, \textit{Fall 2019}.
  \item	{\tt ECO334} -- Political Economy, \textit{Winter 2019.}
  \item	{\tt ECO320} -- Economics and the Law, \textit{Winter 2019}.
  \item	{\tt ECO101} -- Principles of Microeconomics, \textit{Fall 2018}.
\end{itemize}

%\subsection*{Other Teaching}
%\begin{itemize}[nosep]
%\item Invited Lecturer: Reach Alliance Workshop on Secondary Research Methods. \textit{Fall 2022, Fall 2023}
%\end{itemize}


\section*{Service}


\begin{itemize}[itemsep=0.5pt]
  \item \textbf{Graduate Students Support Working Group} \textit{2024}.
  \item \textbf{Graduate Appeals Committee} \textit{2023 -- 2024}.
  \item \textbf{Department Chair Search Committee} \textit{2022}.
  \item \textbf{Graduate Student Mentor} \textit{2021-2022}.
  \item \textbf{Graduate Economics Union}
  \begin{itemize}[nosep, topsep=-1em]
  \item Co-President, \textit{2020 -- 2021}.
  \item Event Coordinator, \textit{2019 -- 2020}.
  \item First Year Representative, {2019 -- 2020}.
  \end{itemize}
%  \item \textbf{Undergraduate Economics Research Program}
%  \begin{itemize}[nosep, topsep=-1em]
%  \item Supervisor: Karen Bernhardt-Walther \textit{2014 -- 2016}.
%  \end{itemize}  
%  \item \textbf{Trinity College Finance Committee}
%  \begin{itemize}[nosep, topsep=-1em]
%  \item Deputy Chair, \textit{2014 -- 2015}.
%  \item Non-Resident Affairs Treasurer, \textit{2014--2016}.
%  \end{itemize}
%
%  \item \textbf{Trinity College Literary Institute}
%  \begin{itemize}[nosep, topsep=-1em]
%  \item Executive Committee Member, \textit{2013 -- 2018}.
%  \end{itemize}
\end{itemize}

\newpage
\section*{References}
\begin{multicols}{2}
\noindent
\textbf{Gustavo J. Bobonis} \\
Department of Economics \\
University of Toronto \\
150 St. George St. \\
Toronto, Ontario \\
M5S 3G7, Canada \\
\href{mailto:gustavo.bobonis@utoronto.ca}{gustavo.bobonis@utoronto.ca} \\[1em]

\textbf{Rob Gillezeau} \\
Rotman School of Management \\
University of Toronto \\
95 St. George St. \\
Toronto, Ontario \\
M5S 3E6, Canada \\
\href{mailto:rob.gillezeau@rotman.utoronto.ca}{rob.gillezeau@rotman.utoronto.ca} \\
\columnbreak

\textbf{Ceren Baysan}\\
Department of Economics \\
University of Toronto \\
150 St. George St. \\
Toronto, Ontario \\
M5S 3G7, Canada \\
\href{mailto:ceren.baysan@utoronto.ca}{ceren.baysan@utoronto.ca} \\[1em]
\end{multicols}

\newpage
\section*{Abstracts}

\subsubsection*{Partisan Elections, Competition, and Candidate Selection: Evidence from School Boards \\(Job Market Paper)}
How do partisan electoral institutions affect local democracy? I study this question in the context of North Carolina school boards, where the state legislature has gradually converted nonpartisan elections to partisan contests since 2014. Using a difference-in-differences design that exploits this staggered rollout, I estimate the causal effect of partisan elections on candidate entry, voter behaviour, and representation. The reforms reshaped competition by creating partisan strongholds, in which candidates were increasingly unlikely to run in districts dominated by the opposing party. As a result, uncontested races rose sharply and candidates with professional experience, such as principals and former board members, were less likely to enter. At the same time, partisan labels polarized voter choice and mobilized turnout, reinforcing strongholds. These dynamics ultimately advantaged Republicans overall and reduced the professional expertise represented on school boards. The findings reveal a central tradeoff: while partisan rules lower information costs for voters, they also weaken competition and diminish the quality of representation in local governance.

\subsubsection*{Improving Judicial Protection in Intimate Partner Violence Cases: The Role of Specialized Courts and Judges \\ (joint with Carolina Arteaga, Gustavo J. Bobonis, and Paola Salardi)}

We study the large-scale implementation of a system of specialized domestic violence courts (SDVCs), an innovation in access to justice programs for potential victims of intimate partner violence (IPV) and offenders. Using individual-level administrative data from the universe of civil domestic violence cases in Puerto Rico during the period 2014-2020, we leverage the staggered opening of SDVCs across judicial regions to examine the consequences for victims' judicial protection and offender recidivism. Access to SDVCs leads to a considerable 8 percentage points increase in the probability that judges issue a protection order and a 1.7 percentage point (15 percent) decrease in victim and offender reappearance rates within one year of the start of the case. Effects are more pronounced for cases in which parties have children in common and in which access to SDVCs is more limited. Linking the case data to administrative and survey data on judges, we show that the priorities of judges assigned to SDVCs play a prominent role in explaining these outcomes.

\subsubsection*{Electoral Cycles in Female Sterilization \\(joint Simeon Nichter)}

Many women across the world face substantial challenges in obtaining access to family planning --- an important problem emphasized by the Sustainable Development Goals. The present study explores electoral cycles in female sterilization, the most prevalent contraceptive method in the world. We focus on Brazil, a country where many women have unmet demands for sterilization and often queue for many months or even years for their surgeries. Qualitative evidence suggests that local politicians manipulate the provision of publicly funded tubal ligation surgeries for political purposes. We analyze the universe of tubal ligation surgeries performed by the public health system, using regression analysis to examine variation across Brazilian municipalities in 1998-2019.  We find that female sterilizations increase 8.8\% during municipal election years. Moreover, they surge during electoral campaigns:  female sterilizations increase 30.5\% in the three months before municipal elections.  Findings are similar when adjusting for overall hospitalizations, which rise less than 1\% during municipal elections. Female sterilizations have more pronounced electoral cycles than do other elective surgeries (including vasectomies), and no cycles are detected for emergency surgeries. Electoral cycles in female sterilization are concentrated among nonwhite Brazilians, who face substantial health disparities. Female sterilizations increase far more during municipal than national elections, and they spike especially in poor municipalities and in the Northeast region.  More broadly, our findings suggest that Brazilian politicians distort the public provision of contraception, a crucial problem not least because family planning is widely deemed a basic human right.

%
%\section*{Publications}
%
%\subsection*{Journal Articles}
%
%\begin{itemize}
%\item A General Mathematical Theory of Depreciation, 1929, {\it Journal
%    of The American Statistical Association} 20, 340--353.
%\item Differential Equations Subject to Error, 1927, {\it Journal of The
%    American Statistical Association}.
%\item Applications of the Theory of Error to the Interpretation of
%  Trends (with H. Working), 1929, {\it Journal of the American
%    Statistical Association}.
%\end{itemize}
%
%\subsection*{Proceedings}
%
%\begin{itemize}
%\item A generalized T-Test and measure of multivariate dispersion,
%  Proc. Second Berkeley Symposium of Mathematical Statistics and
%  Probability, 1951.
%\end{itemize}
%
%\bigskip
%
%% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}
